The force-free magnetosphere of a Kerr black hole: the role of boundary conditions

### 2018-06-28 paper/ms.tex
save

>>>>

The Blandford-Znajek (BZ) mechanism \cite{Blandford1977} is believed to be
one of most efficient ways to extract rotation energy from spinning black holes (BHs),
which operates in BH systems on all mass scales, from the stellar-mass BHs of gamma-ray
bursts to the supermassive BHs of active galactic nuclei. In the past decade,
we have studied the BZ mechanism from different approaches and the cross-check among
these different approaches has facilitate substantial progress in understanding the BZ mechanism.
: general relativistic
magnetohydrodynamic (GRMHD) simulations \cite{Komissarov2001,Komissarov2004,Komissarov2004e, McKinney2004},
analytic solutions \cite{Tanabe2008,Pan2015,Pan2015b, Gralla2014, Gralla2015, Penna2015}
and numerical solutions  \cite{Contopoulos2013,Nathanail2014,Mahlmann2018},
and all these different approaches give quantitative agreement for simple magnetic field configurations,
e.g.,

Uniform field solution \cite{Komissarov2004e, Komissarov2005, Komissarov2007,Palenzuela2010,Paschalidis2013,
Yang2015,Carrasco2017}
